\subsection{Usability}
Usability is being reviewed by using information gathered with the questionnaires. Two constructs were built from the multiple choice questions: \textsc{system usefulness} 
and \textsc{interface quality}. Furthermore some information can be extracted from the open question. 

A strong main effect of interaction device was found on the perceived system usefulness and interface quality. The keyboard-mouse combination scored significantly higher than 
the Leap Motion. This means that the users experienced the keyboard and mouse the be more usable than the Leap Motion independent of the order of experiment. 

The open questions give some insight why this is the case. Corresponding with the behavioral data the participants performed poorly using the Leap Motion. They reported the 
tasks to be difficult to nearly impossible when using the Leap Motion. In general the task objective and the concept of the interaction (how to operate the mouse/Leap Motion) 
was clear. The poor efficiency and speed of the Leap Motion resulted in poor usability. 

Other noteworthy aspects were the physical effort needed to use the Leap Motion and fun-factor. At several occasions in the questionnaire participants reported that physical 
efforts needed to operate the Leap Motion was too high. Besides all negative responses on the Leap Motion the fun factor remained.

All participants saw potential in the Leap Motion. Users would appreciate it better if the efficiency and the speed would improve and when it the setting is not work 
related e.g. in gaming. 
